
## Cost-effectiveness acceptability curve

The _Cost-Effectiveness Acceptability Curve_ (CEAC) estimates the probability of cost-effectiveness, for different willingness to pay thresholds. The CEAC is used to evaluate the uncertainty associated with the decision-making process, since it quantifies the degree to which a treatment is preferred. This is measured in terms of the difference in utilities, normally the incremental benefit. Effectively, the CEAC represents the proportion of simulations in which $t=1$ is associated with a higher utility than $t=0$.

The following graph shows the cost-effectiveness acceptability curve (CEAC). The CEAC represents the proportion of 'potential futures' in which the reference intervention is estimated to be more cost-effective than the comparator. Thus, it can be interpreted as the 'probability of cost-effectiveness'. 


```{r, echo=echo, fig.width=4.6, fig.height=4.6, fig.align=align, warning=FALSE, message=FALSE, comment=NA}
ceac.plot(m)
```

## Cost-effectiveness acceptability frontier
In addition to the CEAC, we can also visualise the uncertainty in the decision-making process using the _Cost-Effectiveness Acceptability Frontier_ (CEAF). The frontier is defined as the maximum value of the probability of cost-effectiveness among all comparators. It is an indication of the uncertainty associated with choosing the cost effective intervention. In other terms, higher frontier values correspond to lower decision uncertainty.


```{r, echo=echo, fig.width=4.6, fig.height=4.6, fig.align=align, warning=FALSE, message=FALSE, comment=NA}
n.ints <- m$n_comparators

if (n.ints == 2) {
  graph <- "base"
  pos <- c(1, 1)
} else {
  graph <- "ggplot2"
  pos <- TRUE
}
ceaf.plot(multi.ce(m), graph = graph)
```
