---
title: "Cost-effectiveness plane"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Cost-effectiveness plane}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.width = 6
)
```

```{r setup, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(BCEA)
library(dplyr)
#library(reshape2)
library(ggplot2)
library(purrr)
```


## Introduction

The intention of this vignette is to show how to plot different styles of cost-effectiveness acceptability curves using the BCEA package.

#### R code

To calculate these in BCEA we use the `bcea()` function.

```{r}
data("Vaccine")

he <- bcea(eff, cost)
```

The plot defaults to `ggplot2` R plotting. Type of plot can be set explicitly using the `graph` argument. In fact, the default graphical engine is set upon loading `BCEA` and can be modified globally using the command `options(bcea.graph="...")`. Choices are `ggplot2`, `base` or `plotly`. Partial matching is also available, so that `gg`, `g`, `pl` or `p` are recognised alteratives to `ggplot2` or `plotly`, respectively.


```{r}
ceplane.plot(he, graph = "base")
ceplane.plot(he, graph = "ggplot2")
# ceac.plot(he, graph = "plotly")
```

Other plotting arguments can be specified such as title, line colours and theme.

```{r}
ceplane.plot(he,
             graph = "ggplot2",
             title = "my title",
             line = list(color = "green", size = 3),
             point = list(color = "blue", shape = 10, size = 5),
             icer = list(color = "orange", size = 5),
             area = list(fill = "grey"),
             theme = theme_linedraw())
```

If you only what the mean point then you can suppress the sample points by passing size `NA`.

```{r}
ceplane.plot(he,
             graph = "ggplot2",
             point = list(size = NA),
             icer = list(size = 5))
```

In the default `ggplo2` version, the formatting of the axes can be easily modify using `ggplot2` facilities, like so.

```{r}
ceplane.plot(he) +
  scale_y_continuous(labels=scales::dollar_format(prefix="£")) 
```

The $x-$ or $y-$ axes can be modified separately using `scale_x_continuous` or `scale_y_continuous`, respectively. See `help(dollar_format)` from the package `scales` for more information.

## Multiple interventions

This situation is when there are more than two interventions to consider.

#### R code

```{r}
data("Smoking")

he <- bcea(eff, cost, ref = 4)
# str(he)
```

Basic plots with defaults.

```{r}
ceplane.plot(he)
ceplane.plot(he, graph="base")
```

The font size can be adjusted using the `text` argument.

```{r}
ceplane.plot(he, graph = "ggplot2", text = list(size = 20))
ceplane.plot(he, graph = "ggplot2", text = list(size = rel(2)))  # relative scaling, double size

# equivalent but more flexible and direct
ceplane.plot(he, graph = "ggplot2") +
  theme(axis.text = element_text(size = 18),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20))
```

Numerous different styling arguments can be provided.

```{r}
ceplane.plot(he,
             graph = "ggplot2",
             title = "my title",
             line = list(color = "red", size = 1),
             point = list(color = c("plum", "tomato", "springgreen"), shape = 3:5, size = 2),
             icer = list(color = c("red", "orange", "black"), size = 5))
```

There are various different ways to reposition the legend.

```{r}
#| fig.width: 7
#| fig.height: 5
#| out.width: 90%

ceplane.plot(he, pos = FALSE) # bottom right
ceplane.plot(he, pos = TRUE)  # bottom left
```


With numeric coordinates we can move the legend within the plot area.
```{r}
#| fig.width: 7
#| fig.height: 5
#| out.width: 90%

ceplane.plot(he, pos = c(0, 0))
ceplane.plot(he, pos = c(0, 1))
ceplane.plot(he, pos = c(1, 0))
ceplane.plot(he, pos = c(1, 1))

ceplane.plot(he, graph = "ggplot2", pos = c(0, 0))
ceplane.plot(he, graph = "ggplot2", pos = c(0, 1))
ceplane.plot(he, graph = "ggplot2", pos = c(1, 0))
ceplane.plot(he, graph = "ggplot2", pos = c(1, 1))
```

Using key words for the corners of the plot area for base R.
```{r}
#| fig.width: 7
#| fig.height: 5
#| out.width: 90%

options(bcea.graph="base")
ceplane.plot(he, pos = "bottomright")
ceplane.plot(he, pos = "topright")
ceplane.plot(he, pos = "topleft")
ceplane.plot(he, pos = "bottomleft")
```

and for ggplot2 this is outside of the plot area on each side.
```{r}
#| fig.width: 7
#| fig.height: 5
#| out.width: 90%

ceplane.plot(he, graph = "ggplot2", pos = "right")
ceplane.plot(he, graph = "ggplot2", pos = "top")
ceplane.plot(he, graph = "ggplot2", pos = "left")
ceplane.plot(he, graph = "ggplot2", pos = "bottom")
```

We can also adjust the layout of the ggplot2 legend to a single line (horizontal) or stacked (vertical). If using this then you also need to give a location as follows.
```{r}
#| fig.width: 7
#| fig.height: 5
#| out.width: 90%

ceplane.plot(he, graph = "ggplot2", pos = "verticaltop")
ceplane.plot(he, graph = "ggplot2", pos = "horizontalbottom")
ceplane.plot(he, graph = "ggplot2", pos = "verticalbottom")
```


### Willingness-to-pay label

For `{ggplot2}` we can modify the willingness-to-pay label e.g. "k = 25000".

The default is

```{r}
ceplane.plot(he, graph = "ggplot2")
```

The simplest argument is to set the value of the willingness-to-pay threshold using `wtp`.

```{r}
ceplane.plot(he, graph = "ggplot2", wtp = 10000)
```

Alternatively, we can pass a list of arguments to `wtp` to modify the appearance of the label.

```{r}
ceplane.plot(he, graph = "ggplot2", wtp = list(value = 10000))
ceplane.plot(he, graph = "ggplot2", wtp = list(value = 10000, color = "blue"))
ceplane.plot(he, graph = "ggplot2", wtp = list(color = "blue"))
ceplane.plot(he, graph = "ggplot2", wtp = list(size = 5))
```

To hide the text assign `size = 0`.

```{r}
ceplane.plot(he, graph = "ggplot2", wtp = list(size = 0))
```

The wtp label is placed at the left hand side of the plot next to the willingness-to-pay line by default. When this would mean the label is off the bottom of the plot it is positioned at the bottom left corner.

```{r}
data("Vaccine")
he <- bcea(eff, cost, ref=2)

ceplane.plot(he, graph = "ggplot2")
ceplane.plot(he, graph = "ggplot2", wtp = 1000, xlim = c(-0.0005, 0.0015))
ceplane.plot(he, graph = "ggplot2", wtp = 10000, xlim = c(-0.0005, 0.0015))
ceplane.plot(he, graph = "ggplot2", wtp = 25000, xlim = c(-0.0005, 0.0015))
ceplane.plot(he, graph = "ggplot2", wtp = 50000, xlim = c(-0.0005, 0.0015))
```

The position of the willingness to pay label can be adjusted using the `label.pos` argument and a logical value.

```{r}
ceplane.plot(he, graph = "ggplot2", wtp = 1000, xlim = c(-0.0005, 0.0015), label.pos = TRUE)
ceplane.plot(he, graph = "ggplot2", wtp = 1000, xlim = c(-0.0005, 0.0015), label.pos = FALSE)
```

A direct way of specifying the position of the label is to use the `wtp` argument and set the `y` value in a list.

```{r}
ceplane.plot(he, graph = "ggplot2", wtp = list(y = 8))
```

For base `R`

```{r}
options(bcea.graph = "base")
ceplane.plot(he)  # default
```

```{r}
ceplane.plot(he, wtp = 1000, xlim = c(-0.0005, 0.0015))
ceplane.plot(he, wtp = 10000, xlim = c(-0.0005, 0.0015))
ceplane.plot(he, wtp = 25000, xlim = c(-0.0005, 0.0015))
ceplane.plot(he, wtp = 50000, xlim = c(-0.0005, 0.0015))
```

```{r}
ceplane.plot(he, wtp = 1000, xlim = c(-0.0005, 0.0015), label.pos = TRUE)
ceplane.plot(he, wtp = 1000, xlim = c(-0.0005, 0.0015), label.pos = FALSE)
```

```{r}
##TODO: not yet implemented ggplot syntax for base R

# ceplane.plot(he, wtp = list(color = "blue"))
# ceplane.plot(he, wtp = list(y = 8))
# ceplane.plot(he, wtp = list(size = 5))
# 
# # to hide text
# ceplane.plot(he, wtp = list(size = 0))
```

<!-- ```{r} -->

<!-- ceac.plot(he, graph = "ggplot2", pos = c(0, 0)) -->

<!-- ceac.plot(he, graph = "ggplot2", pos = c(0, 1)) -->

<!-- ceac.plot(he, graph = "ggplot2", pos = c(1, 0)) -->

<!-- ceac.plot(he, graph = "ggplot2", pos = c(1, 1)) -->

<!-- ``` -->

<!-- Define colour palette. -->

<!-- ```{r} -->

<!-- mypalette <- RColorBrewer::brewer.pal(3, "Accent") -->

<!-- ceac.plot(he, -->

<!--           graph = "base", -->

<!--           title = "my title", -->

<!--           line = list(colors = mypalette), -->

<!--           pos = FALSE) -->

<!-- ceac.plot(he, -->

<!--           graph = "ggplot2", -->

<!--           title = "my title", -->

<!--           line = list(colors = mypalette), -->

<!--           pos = FALSE) -->

<!-- ``` -->

<!-- ### Pair-wise comparisons -->

<!-- Again, without loss of generality, if we assume that we are interested in intervention $i=1$, the we wish to calculate -->

<!-- $$ -->

<!-- p(NB_1 = \max\{NB_i : i \in S\} | k) -->

<!-- $$ -->

<!-- This can be approximated by the following. -->

<!-- $$ -->

<!-- \frac{1}{N} \sum_j^N \prod_{i \in S} \mathbb{I} (k \Delta e_{1,i}^j - \Delta c_{1,i}^j) -->

<!-- $$ -->

<!-- #### R code -->

<!-- In BCEA we first we must determine all combinations of paired interventions using the `multi.ce()` function. -->

<!-- ```{r} -->

<!-- he <- multi.ce(he) -->

<!-- ``` -->

<!-- We can use the same plotting calls as before i.e. `ceac.plot()` and BCEA will deal with the pairwise situation appropriately. -->

<!-- Note that in this case the probabilities at a given willingness to pay sum to 1. -->

<!-- ```{r} -->

<!-- ceac.plot(he, graph = "base") -->

<!-- ceac.plot(he, -->

<!--           graph = "base", -->

<!--           title = "my title", -->

<!--           line = list(colors = "green"), -->

<!--           pos = FALSE) -->

<!-- mypalette <- RColorBrewer::brewer.pal(4, "Dark2") -->

<!-- ceac.plot(he, -->

<!--           graph = "base", -->

<!--           title = "my title", -->

<!--           line = list(colors = mypalette), -->

<!--           pos = c(0,1)) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- ceac.plot(he, -->

<!--           graph = "ggplot2", -->

<!--           title = "my title", -->

<!--           line = list(colors = mypalette), -->

<!--           pos = c(0,1)) -->

<!-- ``` -->

<!-- ```{r echo=FALSE} -->

<!-- # create output docs -->

<!-- # rmarkdown::render(input = "vignettes/ceac.Rmd", output_format = "pdf_document", output_dir = "vignettes") -->

<!-- # rmarkdown::render(input = "vignettes/ceac.Rmd", output_format = "html_document", output_dir = "vignettes") -->

<!-- ``` -->
