---
title: "Contour Plots"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Contour Plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.width = 6
)
```

```{r setup, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(BCEA)
library(dplyr)
#library(reshape2)
library(ggplot2)
library(purrr)
```


## Introduction

The intention of this vignette is to show how to plot different styles of contour plot using the BCEA package and the `contour()` and `contour2()` functions.


#### R code

To calculate these in BCEA we use the `bcea()` function.

```{r}
data("Vaccine")
he <- bcea(eff, cost, ref = 2)
```

The plot defaults to `ggplot2` R plotting. Type of plot can be set explicitly using the `graph` argument. In fact, the default graphical engine is set upon loading `BCEA` and can be modified globally using the command `options(bcea.graph="...")`. Choices are `ggplot2`, `base` or `plotly`. Partial matching is also available, so that `gg`, `g`, `pl` or `p` are recognised alteratives to `ggplot2` or `plotly`, respectively.

```{r}
contour(he, graph = "base")
contour(he, graph = "ggplot2")
# ceac.plot(he, graph = "plotly")
```

User-defined contour levels can be provided.
The `levels` and `nlevels` arguments specify the quantiles or number of levels.
The base R levels arguments are kept for back-compatibility and the `ggplot2` style arguments are used in the associated plot.

```{r}
contour(he, levels = c(0.2, 0.8), graph="base")
contour(he, graph = "ggplot2", contour = list(breaks = c(0.2, 0.8)))
```


Other plotting arguments can be specified such as title, line colour and thickness and type of point.

```{r}
contour(he,
        graph = "ggplot2",
        title = "my title",
        point = list(color = "blue", shape = 2, size = 5),
        contour = list(linewidth = 2))
```

```{r}
contour(he,
        graph = "base",
        title = "my title",
        point = list(color = "blue", shape = 2, size = 2),
        contour = list(linewidth = 2))
```

Alternatively, the `contour2()` function is essentially a wrapper for `ceplane.plot()` with the addition of contour lines.

```{r}
contour2(he, graph = "base")
contour2(he, graph = "ggplot2")
# ceac.plot(he, graph = "plotly")
```

Other plotting arguments can be specified in exactly the same way as above.

```{r}
contour2(he,
         graph = "ggplot2",
         title = "my title",
         point = list(color = "blue", shape = 10, size = 5),
         contour = list(linewidth = 2))
```

```{r}
contour2(he,
         graph = "base",
         title = "my title",
         point = list(color = "blue", shape = 2, size = 3),
         contour = list(linewidth = 4))
```


## Multiple interventions

This situation is when there are more than two interventions to consider.

#### R code

```{r}
data("Smoking")
he <- bcea(eff, cost, ref = 4)
# str(he)
```

Because there are multiple groups then the quadrant annotation is omitted.

```{r}
contour(he, graph = "base")
contour(he, graph = "ggplot2")
```

The `scale` argument determines the smoothness of the contours.

```{r}
contour(he, scale = 0.9, graph = "base")
contour(he, graph = "ggplot2", scale = 0.9)  ##TODO: what is the equivalent ggplot2 argument?
```

The quantiles or number of levels.

```{r}
contour(he, nlevels = 10, graph = "base")
contour(he, graph = "ggplot2", contour = list(bins = 10))
```

```{r}
contour(he, levels = c(0.2, 0.8), graph = "base")
contour(he, graph = "ggplot2", contour = list(breaks = c(0.2, 0.8)))
```

```{r}
contour(he,
        graph = "ggplot2",
        title = "my title",
        line = list(color = "red", size = 1),
        point = list(color = c("plum", "tomato", "springgreen"), shape = 3:5, size = 2),
        icer = list(color = c("red", "orange", "black"), size = 5),
        contour = list(linewidth = 2))
```

```{r}
contour(he,
        graph = "base",
        title = "my title",
        line = list(color = "red", size = 1),
        point = list(color = c("plum", "tomato", "springgreen"), shape = 3:5, size = 2),
        icer = list(color = c("red", "orange", "black"), size = 5),
        contour = list(size=2))
```

Again, this applies to the `contour2()` version of contour plot too.

```{r}
contour2(he, wtp = 250, graph = "base")
contour2(he, wtp = 250, graph = "ggplot2")
```

The styling of the plot for multiple comparisons can specifically change the colour and point type for each comparison.

```{r}
contour2(he, wtp = 250,
         graph = "ggplot2",
         title = "my title",
         line = list(color = "red", size = 1),
         point = list(color = c("plum", "tomato", "springgreen"), shape = 3:5, size = 2),
         icer = list(color = c("red", "orange", "black"), size = 5),
         contour = list(linewidth = 2))
```

```{r}
contour2(he, wtp = 250,
         graph = "base",
         title = "my title",
         line = list(color = "red", size = 1),
         point = list(color = c("plum", "tomato", "springgreen"), shape = 3:5, size = 2),
         icer = list(color = c("red", "orange", "black"), size = 5),
         contour = list(linewidth = 4))
```

Reposition legend.

```{r}
contour(he, pos = FALSE, graph = "base")    # bottom right
contour(he, pos = c(0, 0), graph = "base")
contour(he, pos = c(0, 1), graph = "base")
contour(he, pos = c(1, 0), graph = "base")
contour(he, pos = c(1, 1), graph = "base")
```


<!-- ```{r echo=FALSE} -->
<!-- # create output docs -->
<!-- # rmarkdown::render(input = "vignettes/ceac.Rmd", output_format = "pdf_document", output_dir = "vignettes") -->
<!-- # rmarkdown::render(input = "vignettes/ceac.Rmd", output_format = "html_document", output_dir = "vignettes") -->
<!-- ``` -->
