---
title: "Paired vs Multiple Comparisons"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Paired vs Multiple Comparisons}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
fig.width = 6
)
```

```{r setup, results='hide', message=FALSE, warning=FALSE, echo=FALSE}
library(BCEA)
library(dplyr)
#library(reshape2)
library(ggplot2)
library(purrr)
```

## Introduction

The intention of this vignette is to show how to plot the CEAC and EIB plots depending on whether we consider all interventions simultaneously or pair-wise against a reference.

## Multiple interventions

This situation is when there are more than two interventions to consider.
Incremental values can be obtained either always against a fixed reference intervention, such as status-quo, or for all comparisons simultaneously.
We will call these a paired comparison or a multiple comparison.

### Against a fixed reference intervention

#### R code

This is the default plot for `ceac.plot()` so we simply follow the same steps as above with the new data set. The default graphical engine is `ggplot2`. Type of plot can be set explicitly using the `graph` argument. In fact, the default graphical engine is set upon loading `BCEA` and can be modified globally using the command `options(bcea.graph="...")`. Choices are `ggplot2`, `base` or `plotly`. Partial matching is also available, so that `gg`, `g`, `pl` or `p` are recognised alteratives to `ggplot2` or `plotly`, respectively.


```{r}
data("Smoking")
he <- bcea(eff, cost, ref = 4, Kmax = 500)
```

```{r fig.height=10}
par(mfrow = c(2,1))
ceac.plot(he, graph = "base")
abline(h = 0.5, lty = 2)
abline(v = c(160, 225), lty = 3)
eib.plot(he, plot.cri = FALSE, graph = "base")
```


### Pair-wise comparisons

#### R code

In _BCEA_ we first we must determine all combinations of paired interventions using the `multi.ce()` function.

```{r}
he.multi <- multi.ce(he)
```

```{r fig.height=10}
par(mfrow = c(2, 1))
ceac.plot(he.multi, graph = "base")
abline(h = 0.5, lty = 2)
abline(v = c(160, 225), lty = 3)
eib.plot(he, plot.cri = FALSE, graph = "base")
```

