---
title: "Info Rank"
output: 
	pdf_document
	word_document
---
```{r, echo=FALSE}
if(input$format=="PDF") {
    align="center"
} else {
    align="default"
}
```

## Info-rank plot
Another way in which the analysis of the value of information (specifically based on the Expected Value of Perfect _Partial_ Information, EVPPI) can be used is to provide an 'overall' assessment of the impact of each single parameter on the decision uncertainty. To this aim, BCEA has a specialised function that produces a plot of the univariate EVPPI for all the parameters of interest (as specified by the user). While this is not ideal, since correlation among parameters and model structure does have an impact on the joint value of the EVPPI (which is not a linear combination of the individual EVPPIs!), the Info-rank plot with all the model parameters ranked can be used as a sort of _Tornado diagram_, a tool often used in deterministic sensitivity analysis.

For each parameter and value of the willingness-to-pay threshold $k$, a barchart is plotted to describe the ratio of EVPPI (specific to that parameter) to EVPI. This represents the relative 'importance' of each parameter in terms of the expected value of information.

```{r, echo=echo,fig.width=4.6, fig.height=4.6,fig.align=align,warning=FALSE,message=FALSE,comment=NA}
# Uses the BCEA function 'CreateInputs' to pre-process the PSA runs and obtain a suitable format
mat=CreateInputs(psa_sims)
IR=info.rank(1:ncol(mat$mat),mat$mat,he=m,wtp=wtp)
if(show.tab==TRUE){IR$rank}
```
